Same as always: I suck at titles

### 2024-12-12 manuscript/manuscript_eb.tex
tidy-stuff

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5173}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Same as always: I suck at titles},
  pdfauthor={Esperanza Badaya1, Robert J. Hartsuiker1, \& Martin Corley2},
  pdflang={en-EN},
  pdfkeywords={filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Whether an individual is perceived as knowledgeable by others can be biased by several, and potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking). The presence of disfluencies, such as filled pauses (e.g., \emph{uh} or \emph{um} in English), elicit evaluations of the speaker as deceitful, less intelligent, or less confident in their knowledge. On the other hand, listeners consider alternative explanations for the speaker to be underinformative: Specifically, non-native speakers are more likely to be forgiven when they fail to be informative. However, whether and how speaker's language profiency affects the interpretation of hesitations and listeners' subsequent behaviour is unclear. In a horse-race betting paradigm, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge. This suggests that previous reported perceptions of knowledgeability elicited explicitly have an impact on how individuals use the information they are given, even in situations when it is not advantageous. Although there is evidence for pragmatic leniance towards non-native speakers, it may be the case that this only applies to failures in language skills that are believed to require high proficiency (e.g., irony), whilst hesitation phenomena may not be subject to such forgiveness. Overall, our results align with a broader body of literature suggesting that the interpretation of hesitation phenomena is not context-dependent.
}

@@

Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008). Speakers can be evaluated not only by what they say but also by how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005). One speech feature consistently found to bias evaluations of the speaker is speech fluency. Speech which includes disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995). Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011). In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually. It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener(Jiang \& Pell, 2015, 2016b, 2016a). Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021). These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993). Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK. Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge. In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. Brennan and Williams (1995) took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).

In a similar vein, speaker identity can itself affect evaluations of both the speaker and the content of speech. In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations. On the one hand, speakers with a foregin accent are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010). Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021). These negative effects triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, or a combination of both (Mai \& Hoffmann, 2013).

On the other hand, there seem to be instances where being a non-native speaker is more advantageous. Fairchild, Mathis, and Papafragou (2020) examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness. Fairchild et al. (2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identities. In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention. Native speakers who were underinformative were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4) (for similar findings, see Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022). Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.

One potential explanation is that non-native speakers are evaluated differently from native speakers due to expectations about their competence. Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018) or why non-native speech is processed more shallowly (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered. For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it is possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including non-native versus native speakers (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.

Recently, Matzinger, Pleyer, and Żywiczyński (2023) explored whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers. In their study, participants listened staged conversations where native and non-native speakers answered trivial questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request. Crucially, Matzinger et al. (2023) manipulated speakers' fluency by manipulating inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses. For requests, long pauses were less likely to be associated with unwillingness for non-native compared to native speakers. However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge. Matzinger et al. (2023) attribute this pattern to different conversational contexts: Requests tap into speakers' cooperativeness, and thus in this context, tuning to the interlocutor's mental state and stereotyping might be more relevant than evaluating the speaker's competence (i.e., knowledge).

As is the case for Matzinger et al. (2023), most studies evaluating the effects of manner of speech on pereptions of the speaker have used explicit ratings. Participants are asked to rate particular traits of speakers or what they say on a scale. Further, these ratings are elicited in non-social contexts, where participants do not have anything at stake. Although these experiments demonstrate that listeners show sensitivity to aspects of speech such as fluency and accent when asked to make explicit judgements about the speaker, they may not explain how listeners evaluate speech implicitly, when to do so is consequential.Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm. In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race. This approach presents two advantages over previous experiments. First, in the horse-race paradigm, participants are not explicitly asked to evaluate a certain trait of the speaker (in this case, how knowledgeable they are). Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge. Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets (Butterworth, 2019). Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are less familiar with the world of horse racing or its technical vocabulary).

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).

@@

All experimental stimuli can be found at \url{https://osf.io/zsut7/}.

@@

We conducted a sensitivity power analysis via data simulation following DeBruine and Barr (2021). We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity. We conducted a 1000 simulations per different combinations of the effect size of the interaction (ranging from small to medium) and the standard deviation of the residuals. In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity. This analysis showed that a sample size of 360 participants ensured enough power to detect a medium or greater effect size.

In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study. Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races. This meant that we recruited 641 participants for a sample of 360. Participants were aged between 18 and 30, born and raised in the United Kingdom, and reported that they did not consider themselves as experts in horse races. Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3). Participants were reimbursed £1.50 for a 10-minutes experiment.

@@

A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (F(7) = 0.5, \emph{p} = .83). An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all \textbar t\textbar{} \textless{} 2). We therefore selected four out of the eight images as visual stimuli.

@@

Based on these results, we further edited the descriptions as some descriptions were more likely to be rated as winning horses. A new sample fo 30 British English speaker rated the edited passages. A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (F(3) = 0.76, \emph{p} = .52), nor in the order in which they were ranked (all \textbar t\textbar{} \textless{} 2). The final set of descriptions for the experiment can be found in Table \ref{tab:tab-horse-description-text}. Each description was paired with one of the four visual stimuli.

@@

We recorded a British English native speaker and a non-native (L1: Italian) English speaker to create the auditory stimuli. Both speakers were female. Passages were recorded one at a time. To elicit naturally disfluent recordings, both speakers were instructed to read the passages silently and then were recorded as they tried to recall the passage from memory. To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation. We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (see Table \ref{tab:tab-horse-description-disfluent}). To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function. The final auditory experimental stimuli consisted, for each speaker, of two descriptions of each horse (one disfluent, one fluent), resulting in sixteen recordings. Description, fluency, speaker, and order of presentation were counterbalanced in a Latin Square design, resulting in 24 lists.

\caption{\label{tab:tab-horse-description-disfluent}Transcriptions of the disfluent horse descriptions.}

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing\newline\indent Word count: 5367}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{figure}
\renewcommand{\cftfigpresnum}{\itshape\figurename\enspace}
\renewcommand{\cftfigaftersnum}{.\space}
\setlength{\cftfigindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cftfignumwidth}{Figure 10.\qquad}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Same as always: I suck at titles},
  pdfauthor={Esperanza Badaya1, Robert J. Hartsuiker1, \& Martin Corley2},
  pdflang={en-EN},
  pdfkeywords={filled pauses, disfluencies, non-native-accented speech, feeling of another's knowing},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Whether an individual is perceived as knowledgeable by others can be biased by several potentially irrelevant factors, ranging from the ephemeral (e.g., how speech is produced) to the situational (e.g., who is speaking). Existing evidence for these effects tends to come from metalinguistic evaluations; here we examine the behavioral consequences of variations in the ways in which spoken messages are produced. Specifically,we investigate how attributions of knowledgeability are influenced by speech fluency, and by whether or not the speaker has a native accent, cues which have been previously shown to bias listeners' evaluations of speakers and what they are saying. We use a novel horse-race betting paradigm, in which participants have to place bets on horses which have been described in short spoken passages. By manipulating the fluency (fluent or disfluent) and accent (native or non-native) with which the descriptions are produced, we show that listeners are less likely to follow advice from a speaker who is disfluent, regardless of whether they are disfluent for reasons other than low knowledge (e.g., nativeness). Overall, our results align with a broader body of literature suggesting that the effects of hesitation phenomena are context-independent. Importantly, we demonstrate that individuals' meta-linguistic judgements can be measured through behavior, suggesting that these judgements have ecological importance beyond the laboratory.
}

@@

Impressions of other people arise naturally and automatically (Uleman et al., 2008). Speakers can be evaluated not only by what they say but also by how they say it. For example, features of speech can affect perceptions of confidence and persuasion (Guyer et al., 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg et al., 2005). Similarly, speech which includes disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995). Interestingly, speech produced with an accent different from one's own---particularly a \emph{foreign} accent---can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek et al., 2011; Gluszek \& Dovidio, 2010; Lev-Ari \& Keysar, 2010; Rakić et al., 2011). Most of these studies, however, have relied on listeners' explicit judgements, which may not reflect everyday language comprehension (Armstrong et al., 1983): Do these judgements arise even when individuals are not asked to make them?. In this study we tested whether listeners' evaluations of a speaker affect their decision-making, and if the co-presence of these two factors (i.e., (dis)fluency and foreign accents) may diminish the negative impact they have individually. In what follows, we briefly describe how speech fluency and accent have been shown to bias listeners' evaluations.

There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and are associated with distinct neural responses in the listener (Jiang \& Pell, 2015, 2016b, 2016a). Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil et al., 2021). These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg et al., 1997; Shriberg \& Lickley, 1993). Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., to rate their \emph{feeling of another's knowing}, FOAK. Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge. In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. Brennan and Williams took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).

In a similar vein, speaker identity can itself affect evaluations of both the speaker and the content of speech. In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations. On the one hand, speakers with a foreign accent are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Lev-Ari \& Keysar, 2010; Boduch-Graba \& Lev-Ari, 2021; but cf.~Souza \& Markan, 2013; Stocker, 2017; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Wetzel, Zufferey, \& Gygax, 2021; Barlow et al., 2024). These negative effects triggered by a speaker's non-nativeness have been primarily accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), whereby difficulties in understanding accented speech decreases processing fluency and consequently elicits negative evaluations about the source.

On the other hand, there seem to be instances where being a non-native speaker is advantageous. Fairchild et al. (2020) examined whether and how failures to provide all relevant information (i.e., being under-informative) are interpreted differently as a function of speakers' nativeness. In four experiments, participants read stories where a speaker (native/non-native) provided a description. Crucially, these descriptions failed to provide all relevant information (e.g., not naming all elements on a display, failing to list all uses of an invention). Participants were then asked to provide an explanation for the speaker's under-informativeness. As descriptions were presented in the written modality, any differences in attributions of under-informativeness would be solely guided by the putative speakers' identities, rather than, for example, by processing fluency. Native speakers who were under-informative were more likely to be rated as unwilling to share the information than under-informative non-native speakers. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4) (for similar findings, see Fairchild \& Papafragou, 2018; Lorenzoni et al., 2022). Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.

One potential explanation for Fairchild et al.'s (2020) results is that non-native speakers are evaluated differently from native speakers due to expectations about their competence. Non-native speakers' accents may invoke stereotypes that suggests that these speakers are less competent linguistically than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect the ways in which their speech is comprehended and interpreted. For example, in the case of under-informativeness, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors, such as ill will, when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi et al., 2022; Caffarra et al., 2018), or how syntactic errors are processed (Hanuíková et al., 2012).

Given that speakers producing speech in their second language are more disfluent (Bergmann et al., 2015; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget et al., 2014), it is possible that a speaker's non-nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold et al., 2007; Barr \& Seyfeddinipur, 2010; Heller et al., 2015), including non-native versus native speakers (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.

Recently, Matzinger et al. (2023) investigated whether listeners' perceptions of why a speaker was disfluent differed for native and non-native speakers. In their study, participants listened to staged conversations in which native and non-native speakers answered trivia questions and requests, and were explicitly asked to rate each speaker's knowledge and confidence (for FOAK) and their willingness to grant the request. Crucially, speakers' fluency was manipulated by having different inter-turn pauses: Answers were prefaced with either short (200 ms) or long (1200 ms) pauses. For requests, long pauses were more likely to be associated with unwillingness for native compared to non-native speakers. However, FOAK ratings did not differ between speakers: Long pauses produced by either speaker were likely to be taken as reflecting low confidence and low knowledge. Matzinger et al.~attributed this pattern to the degree with which a speaker's mental state is relevant across conversational contexts.

As is the case for Matzinger et al. (2023), most studies evaluating the effects of manner of speech on perceptions of the speaker have used explicit ratings. Participants are asked to rate particular traits of speakers or what they say on a scale. Explicit measures as those are more likely to be affected by factors such as self-presentation and less likely to reflect how individuals would behave (Greenwald et al., 2002). In contrast, implicit measures overcome these obstacles while still being able to predict behaviours: For example the Implicit Association Test can predict racist behaviours (McConnell \& Leibold, 2001; although see Payne \& Hannay, 2021 for whether IAT scores are better conceptualised as an aggregation rather than at the individual level). In the case of evaluations about the speaker, they tend to be elicited in non-social contexts: Participants are either overhearers (e.g., Matzinger et al., 2023) or simply attend to a previously recorded speaker (Brennan \& Williams, 1995; Ip \& Papafragou, 2022; e.g., Lev-Ari \& Keysar, 2010). Further, in these experiments, participants have nothing at stake i.e., they are evaluating the speaker, but they do not have to perform any behaviour following the utterance they just heard. While experiments eliciting metalinguistic judgements shed light on what factors may affect how a speaker is perceived, the lack of interaction on participant's behalf entails that these findings may not explain how listeners evaluate speech implicitly, when to do so is consequential.

Here, we propose an implicit measurement of listeners' assessments of the speaker's certainty, using a horse-race paradigm. In this task, participants listen to a set of speakers provide descriptions of horses, and are asked to distribute virtual tokens as `bets' on each horse's likelihood of winning a putative race. This approach presents two advantages over previous experiments. First, in the horse-race paradigm, participants are not explicitly asked to evaluate a specific trait of the speaker (in this case, how knowledgeable they are). Instead, we take participants' allocations of `betting money' as an indirect measurement of their perceptions of speakers' knowledge. Indeed, pilot studies have shown that individuals are sensitive to this manipulation and that disfluent information leads to smaller bets (Butterworth, 2019). Second, horse races provide a scenario where individuals can make decisions based on what they are told, but the content of speech itself may not be informative for many individuals (in that participants are not familiar with the world of horse racing or its technical vocabulary).

In a pre-registered study, we set up to test whether and how perceptions of knowledgeability are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to speaker identity when making judgements about knowledge and confidence following disfluent speech, then descriptions peppered with disfluencies provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for this speaker compared to disfluent descriptions provided by a non-native speaker. The non-native disfluent descriptions may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).

@@

Our pre-registration, all experimental stimuli and scripts can be found at \url{https://osf.io/zsut7/}. Deviations from the original pre-registration (e.g., additional analysis) are marked as such.

@@

We conducted a sensitivity power analysis via data simulation following DeBruine and Barr (2021). We explored the required number of participants for a study with a power higher than .8 for the interaction between fluency and speaker identity. We conducted 1000 simulations per different combinations of the effect size of the interaction (ranging from small to medium) and the standard deviation of the residuals. In this analysis, we assumed a medium effect size of fluency and no effect of speaker identity. This analysis showed that a sample size of 360 participants ensured enough power to detect a medium or greater effect size.

In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could take part in the study. Further, we would exclude from analyse data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four of a 9-point scale (see Procedure section), or considered themselves experts in horse races. This meant that we recruited 641 participants for a sample of 360 (N = 268 rated the audio lower than four, 9 reported the manipulation, 11 rated themselves as experts in horse races). Participants were aged between 18 and 30, and born and raised in the United Kingdom. Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the University of Edinburgh PPLS Ethics Committee (ref no 133-2223/3). Participants were reimbursed £1.50 for a 10-minutes experiment.

@@

A one-way repeated measures ANOVA showed that there were no differences in how likely each horse was thought to be to win a race (\(F(7, 72) = 0.50\), \(p = .832\), \(\hat{\eta}^2_G = .046\), 90\% CI \([.000, .050]\)). An ordinal logistic regression showed that none of the horses were more likely to be ranked differently from the others (all \textbar t\textbar{} \textless{} 2). We therefore selected four out of the eight images as visual stimuli.

@@

A one-way repeated measures ANOVA showed that some descriptions were more likely to be rated as winning horses (\(F(3, 116) = 10.64\), \(p < .001\), \(\hat{\eta}^2_G = .216\), 90\% CI \([.104, .311]\)). Therefore, we edited those passages and had a new sample of 30 British English speaker rate them. A one-way repeated measures ANOVA showed no differences in each horse's rated likelihood of winning a race (\(F(3, 116) = 0.76\), \(p = .516\), \(\hat{\eta}^2_G = .019\), 90\% CI \([.000, .057]\)), nor in the order in which they were ranked (all \textbar t\textbar{} \textless{} 2). The final set of descriptions for the experiment can be found in Table \ref{tab:tab-horse-description-text}. Each description was paired with one of the four visual stimuli.

@@

We recorded a British English native speaker (Darrington area) and a non-native (L1: Italian) English speaker to create the auditory stimuli. Both speakers were female and of similar age. Passages were recorded one at a time. To elicit naturally disfluent recordings, both speakers were instructed to read the passages silently and then were recorded as they tried to recall the passage from memory. To avoid differences between the descriptions provided by the speakers, they were allowed to look at the descriptions as they spoke if they could not remember the continuation. We edited these recordings using Audacity to ensure that the recordings of each speaker had similar numbers of disfluencies in similar locations, by cross-splicing different recordings (recordings can be found on OSF). To create the fluent counterpart of each description, filled and mid-utterance silent pauses were excised, and elongations and between-clause silent pauses were reduced using the `Tempo' function. The final auditory experimental stimuli consisted, for each speaker, of two descriptions of each horse (one disfluent, one fluent), resulting in sixteen recordings. Description, fluency, speaker, and order of presentation were counterbalanced in a Latin Square design, resulting in 24 lists.
